|

### 2021-02-22 manuscript/article.Rmd
WIP

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)
# Install required packages
pkgs <- c('tidyverse', 'magrittr', 'lmtest',
          'estimatr', 'sandwich', 'stargazer',
          'gridExtra', 'WeightIt', 'robustHD', 
          'kableExtra', 'lfe')

@@

# Load data
load('../data/incentives_healthcare.RData')
```

@@

\noindent \textbf{Background}. Mosquito control strategies are the primary
means to reduce \textit{Aedes aegypti} infections worldwide. However,
insecticide spraying is conducted inconsistently across the developing world.
Recent studies indicate that financial incentives may increase the productivity
of health personnel, yet there is little evidence on the impact of monetary
rewards on \textit{A. aegypti}-reduction programmes. We evaluated whether
individual and collective financial incentives improves the performance of
healthcare workers fighting \textit{A. aegypti}, as well as their effect on
city-level numbers of dengue hospitalisations.

\noindent \textbf{Methodology/Principal findings}. We hired and trained
subjects to visit households, find \textit{A. aegypti} breeding sites, and kill
mosquito larvae in the city of Rio Verde, Brazil. In our randomised field
trial, we provided individual and team bonuses to two treatment groups, while
the control group received a flat compensation for completing their tasks.
Financial bonuses increased the number of cleaned breeding sites in both
treatment groups (individual and team bonuses) and the collective treatment
also improved larvae extermination. The intervention lowered dengue
hospitalisations in 10.3\%, but the result was not consistent across all model
specifications.

@@

The intervention took place on the 5^th^ of May, 2018. We randomly assigned
subjects into three groups and directed each group to separate headquarters to
avoid spillovers. In the control group (n = `r as.numeric(table(prodfr$D)[1])`), we told participants that
they would receive a flat payment regardless of their performance (BRL 110 /
USD 25 per subject). In the individual treatment group (n = `r as.numeric(table(prodfr$D)[2])`), we informed
subjects that we would rank each subject separately and double the compensation
for those who performed above the sample median (BRL 220 / USD 50 per subject).
In the collective treatment group (n = `r as.numeric(table(prodfr$D)[3])`), we explained that we would rank
the performance of each group and double the payment for those teams whose
results were higher than the sample median (BRL 220 / USD 50 per subject).
Participants worked in pairs and were aware of other groups, but they did not
know about the different treatment conditions. The teams received a leaflet
with a map of the area they should cover. Each route included around 120 houses
in two or three blocks.

@@

The intervention lowered dengue incidence in 10.3% (CI: [-18.9%, -1.6%]) if we take
both treatments together and compare them with the control group. The result is
consistent around fewer weeks before and after the intervention, but it does
not reach conventional levels of statistical significance. This suggests that
the treatment effect is probably small.

@@

In our second model, we measure the effect of reward schemes on the number of
hospitalisations per census tract. Table \ref{tab:census} shows hospitalisation
counts before the intervention, and then 15, 30, 60, 90, and between 30 to 60
days after the treatment.\footnote{There were 139 Census Tracts analyzed by the 96 pairs. This because 43 pairs worked in more than one Census tract at once.}

>>>>

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)

# Install required packages
pkgs <- c("tidyverse", "magrittr", "lmtest",
          "estimatr", "sandwich", "stargazer",
          "gridExtra", "WeightIt", "robustHD",
          "kableExtra", "lfe", "fixest")

@@

# Load data
load("../data/incentives_healthcare.RData")
```

@@

\noindent \textbf{Background}. Mosquito control is the primary means to reduce
\textit{Aedes aegypti} infections worldwide. However, programmes such as
insecticide spraying and elimination of breeding sites are conducted
inconsistently in many developing nations. Recent studies indicate that
financial incentives may increase the productivity of health personnel, yet
there is little evidence about the impact of monetary rewards on \textit{A.
aegypti}-reduction strategies. We evaluated whether individual and collective
financial incentives improve the performance of healthcare workers fighting
\textit{A. aegypti}, as well as their effect on city-level numbers of dengue
hospitalisations.

\noindent \textbf{Methodology/Principal findings}. We hired and trained
subjects to visit households, find \textit{A. aegypti} breeding sites, and kill
mosquito larvae in the city of Rio Verde, Brazil. In our randomised field
trial, we provided individual and team bonuses to two treatment groups, and
offered a flat compensation to the control group for completing their tasks.
Financial rewards increased the number of cleaned breeding sites in both
treatment groups (individual and team bonuses) and the collective treatment
also improved larvae extermination. The intervention lowered dengue
hospitalisations in 10.3\%, but the result was not consistent across all model
specifications.

@@

The intervention took place on the 5^th^ of May, 2018. We randomly assigned
subjects into three groups and directed each group to separate headquarters to
avoid spillovers. In the control group ($n = $ `r as.numeric(table(prodfr$D)[1])`), we told participants that
they would receive a flat payment regardless of their performance (BRL 110 /
USD 25 per subject). In the individual treatment group ($n = $ `r as.numeric(table(prodfr$D)[2])`), we informed
subjects that we would rank each subject separately and double the compensation
for those who performed above the sample median (BRL 220 / USD 50 per subject).
In the collective treatment group ($n = $ `r as.numeric(table(prodfr$D)[3])`), we explained that we would rank
the performance of each group and double the payment for those teams whose
results were higher than the sample median (BRL 220 / USD 50 per subject).
Participants worked in pairs and were aware of other groups, but they did not
know about the different treatment conditions. The teams received a leaflet
with a map of the area they should cover. Each route included around 120 houses
in two or three blocks.

@@

The intervention lowered dengue incidence in `r round(as.numeric(coef(mod[[4]])[4])*100, 1)`% (CI: [`r round(tidy(mod[[4]], conf.level = 0.9, conf.int = T)$conf.low[4]*100, 1)`%, `r round(tidy(mod[[4]], conf.level = 0.9, conf.int = T)$conf.high[4]*100, 1)`%]) if we take
both treatments together and compare them with the control group. The result is
consistent around fewer weeks before and after the intervention, but it does
not reach conventional levels of statistical significance. This suggests that
the treatment effect is probably small.

@@

In our second model, we measure the effect of reward schemes on the number of
hospitalisations per census tract. Table \ref{tab:census} shows hospitalisation
counts before the intervention, and then 15, 30, 60, 90, and between 30 to 60
days after the treatment.
